---
title: "BOU BONDS Forecast"
author: "Africano Byamugisha"
date: "3/7/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_libraries}
# LIBRARIES
pacman::p_load(
  dplyr,
  rvest,
  data.table,
  tm,
  readxl,
  httr
)
```


# ARIMA Model

The justification for using an ARIMA model is that it is a well-established and widely used method for time series forecasting, particularly for data that exhibit certain patterns such as trend and seasonality. In the case of bond yield to maturity data, we often see trends and seasonality in the data, which can be captured by an ARIMA model.

Furthermore, ARIMA models are able to capture the autocorrelation in the time series data, which is a key feature of financial data. Autocorrelation means that the current value of the yield to maturity is related to the previous values, which can be modeled using lagged values in the ARIMA model.

Overall, ARIMA models provide a flexible and powerful framework for forecasting time series data, including bond yield to maturity data. However, as mentioned earlier, it's important to compare the accuracy of different models and select the one that performs best for the specific dataset and forecasting horizon.

