---
title: "BOU Web Scrapping"
author: "Africano Byamugisha"
date: "3/7/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_libraries}
# LIBRARIES
pacman::p_load(
  dplyr,
  rvest,
  data.table,
  tm,
  readxl,
  httr
)
```


# Description
- This code first uses the rvest package to scrape the webpage for links to the daily excel files. 
- It then extracts the links and titles and stores them in a data frame. 
- The DT package is used to combine the excel files into one data table, which is then written to a new excel file using the writexl package.


# scrape the webpage for links
```{r}
url <- "https://www.bou.or.ug/bou/bouwebsite/FinancialMarkets/Closing-TBondsPrices-Yield.html"
webpage <- read_html(url)
```


# extract links and titles
```{r}
links <- webpage %>% 
html_nodes(".ap-linksequence a") %>%
  html_attr("href")

Date <- webpage %>%
  html_nodes(".ap-linksequence a") %>%
  html_text()

remove_words <- c("T-Bonds as at ","TBonds as at ", ".xlsx","T-Bonds-as-at-","Bonds-as-at-")
Date <- removeWords(Date, remove_words)

```


# create a data frame of links and titles
```{r}

df_links <- data.frame(Date,links)

for(i in 1:nrow(df_links)){
  df_links$links[i] <- paste0("https://www.bou.or.ug",df_links$links[i])
}
```

# read excel files into a comined data frame


```{r}

merge_dt <- data.frame()

for (i in seq_len(nrow(df_links))) {
  tryCatch({
    # Download the Excel file from the link and save it to a temporary file
    if(endsWith(df_links$links[i], ".xlsx")){
      temp_file <- tempfile(fileext = ".xlsx")
      GET(df_links$links[i], write_disk(temp_file))
    } else if(endsWith(df_links$links[i], ".xls")) {
      temp_file <- tempfile(fileext = ".xls")
      GET(df_links$links[i], write_disk(temp_file))
    } else {
      warning(sprintf("File type not recognized in link %d, skipping", i))
      return()
    }
    
    # Find the sheet that matches the name "Bonds as at"
    sheets <- excel_sheets(temp_file)
    target_sheet <- grep("Bonds as at", sheets, ignore.case = TRUE)
    if (length(target_sheet) == 0) {
      warning(sprintf("No sheet matching 'Bonds as at' found in link %d, skipping", i))
      return()
    } else if (length(target_sheet) > 1) {
      warning(sprintf("Multiple sheets matching 'Bonds as at' found in link %d, using the first one", i))
      target_sheet <- target_sheet[1]
    } else {
      target_sheet <- sheets[target_sheet]
    }
    
    # Read the data from the target sheet
    if(endsWith(temp_file, ".xlsx")){
      temp_dt <- read_excel(temp_file, sheet = target_sheet, range = cell_cols("A:B"),
                            col_names = TRUE, col_types = c("date", "numeric"), .name_repair = toupper)
    } else if(endsWith(temp_file, ".xls")) {
      temp_dt <- read_excel(temp_file, sheet = target_sheet, range = cell_cols("A:B"),
                            col_names = TRUE, col_types = c("date", "numeric"), .name_repair = toupper)
    }
    
    # Add the report date to the data frame
    temp_dt$REPORT_DATE <- df_links$Date[i]
    
    # Merge the data into the final data frame
    merge_dt <- bind_rows(merge_dt, temp_dt)
  }, error = function(e) {
    warning(sprintf("Error in link %d: %s, skipping", i, e$message))
  })
}

```

# Clean Up the data

```{r}

dt <- merge_dt
colnames(dt) <- c("maturity_date", "yield_to_maturity", "report_date")

dt <- dt %>% 
select(report_date, maturity_date, yield_to_maturity)

# Convert "report_date" to date format
dt$report_date <- dmy(str_remove_all(dt$report_date, "(?<=\\d)(st|nd|rd|th)"))
dt$report_date <- as.Date(dt$report_date)

# Convert "maturity_date" to date format
dt$maturity_date <- format(dt$maturity_date, "%d/%m/%Y")
dt$maturity_date <- dmy(dt$maturity_date)
dt$maturity_date <- as.Date(dt$maturity_date)

dt <- dt %>% 
  mutate(
    maturity_date = as.Date(gsub("^19", "20", maturity_date), format = "%Y-%m-%d"),
    time_to_maturity = as.numeric(difftime(maturity_date, report_date,units = "days"))
    ) %>%
  na.omit() %>%
  arrange(dt_mod,maturity_date,desc = F)
```




# write the combined table to a new excel file
```{r save_file}

if (file.exists("combined_data.xlsx")) {
  file.remove("combined_data.xlsx")
}

writexl::write_xlsx(dt, "combined_data.xlsx")

```

